The Analogue Method for Precipitation Forecasting: Finding Better Analogue Situations at a Sub-Daily Time Step

### 2015-12-15 Moving temporal window - HESS/template.tex
Writing the Moving temporal window.

\runningtitle{Moving Temporal Window in the AM}

@@

\begin{table}[htb]
	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive. The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level (N$_{1}$), which are here different. The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{N$_{2}$} & \textbf{CRPSS} \\
			\hline
			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 60 & 25 & 34.31 \\
			Zermatt & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 55 & 25 & 28.28 \\
			Visp & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 45 & 25 & 28.85 \\
			Montana & 5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 55 & 30 & 36.11 \\
			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
			Aigle & 7.5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z-2MI}
\end{table}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.2cm]{figures/changes_S1_value.pdf} \\
		\includegraphics[width=8.3cm]{figures/changes_S1_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the mean S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue. (top) Quantiles of the S1 distributions with (06h) and without (24h) the sliding window. (bottom) Quantiles of the relative improvements of the S1 criteria when using the sliding window.}
	\label{fig:changes_S1}
\end{figure}

@@

\subsection{Changements du critère du second niveau d'analogie}

Lorsque nous considérons le second niveau d'analogie de la méthode R2, les situations candidates retenues ne sont pas plus nombreuses, mais les dates peuvent avoir changé. Ainsi, une réduction, mais également une augmentation du critère RMSE sont possibles. La Figure \ref{fig:Graphique_fenetre_glissante_chmts_RMSE}, pour la station d'Ulrichen, présente une très légère amélioration du critère de manière globale. Contrairement au critère S1, les quantiles des gains du RMSE sont répartis de manière relativement symétrique autour de zéro, ce qui révèle l'occurrence de pertes. À nouveau, les résultats des autres stations sont proches, avec un gain médian à zéro pour les premières analogues et croissant par la suite, mais jamais négatif.

\begin{figure}[htb]
	\begin{center}$
		\begin{array}{c}
		\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_val.pdf} \\
		\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_gain.pdf}
		\end{array}$
	\end{center}
	\caption{Synthèse des changements sur le critère RMSE à la station d'Ulrichen, pour les différentes analogues du second niveau d'analogie, dû à la fenêtre temporelle glissante. (gauche) Quantiles de la distribution des valeurs de RMSE avec (06h) et sans (24h) la fenêtre glissante. (droite) Quantiles des gains sur le critère RMSE par l'utilisation de la fenêtre glissante.}
	\label{fig:Graphique_fenetre_glissante_chmts_RMSE}
\end{figure}

\section{Conséquences sur les scores de performance}

@@

\begin{table}[htb]
	\caption{Gain en compétence du CRPS sur les deux niveaux d'analogie dû à l'introduction de la fenêtre temporelle glissante.}
	\begin{center}
		\begin{tabular}{l r r r r r r r r}
			\hline
			\multirow{3}{*}{\textbf{Station}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R1}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R2}} \\
			& \multicolumn{ 2}{c}{\textbf{fenêtre temp}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} & \multicolumn{ 2}{c}{\textbf{fenêtre temp}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} \\
			& \multicolumn{1}{c}{\textbf{std}} & \multicolumn{1}{c}{\textbf{gliss.}} &  &  & \textbf{std} & \textbf{gliss.} &  & \\ 
			\hline
			Ulrichen & 29.37 & 31.12 & 1.74 & \textbf{5.93} & 33.24 & 35.44 & 2.20 & \textbf{6.63} \\ \hline
			Zermatt & 22.20 & 24.34 & 2.14 & \textbf{9.64} & 26.95 & 28.92 & 1.97 & \textbf{7.31} \\ \hline
			Visp & 23.23 & 24.39 & 1.16 & \textbf{5.00} & 27.77 & 29.42 & 1.64 & \textbf{5.92} \\ \hline
			Montana & 30.79 & 31.59 & 0.80 &\textbf{ 2.60} & 34.77 & 36.30 & 1.53 & \textbf{4.39} \\ \hline
			Sion & 24.78 & 25.35 & 0.57 & \textbf{2.31} & 29.36 & 31.07 & 1.71 & \textbf{5.82} \\ \hline
			Aigle & 30.57 & 31.78 & 1.21 & \textbf{3.95} & 35.95 & 38.11 & 2.16 & \textbf{6.00} \\ \hline
		\end{tabular}
	\end{center}
	\label{tab:fenetre_glissante:Gains_CRPSS}
\end{table}

@@

\begin{table}[htb]
	\caption{Paramètres pour les champs de géopotentiel à 500~hPa et 1000~hPa et compétence de la méthode R1 après calibration pour la fenêtre temporelle glissante.}
	\begin{center}
		\begin{tabular}{l c c c c c c c c }
			\hline
			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \textbf{CRPSS} & \multirow{2}{*}{\textbf{$\Delta$}} & \textbf{Gain} \\ 
			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} &  & \textbf{(\%)} & & \textbf{(\%)} \\ 
			\hline
			Ulrichen & 0 & 17.5 & 42.5 & 7.5 & 50 & 31.58 & 2.20 & \textbf{7.50} \\ \hline
			Zermatt & 0 & 17.5 & 40 & 10 & 55 & 24.71 & 2.51 & \textbf{11.32} \\ \hline
			Visp & -2.5 & 22.5 & 40 & 10 & 55 & 25.08 & 1.85 & \textbf{7.96} \\ \hline
			Montana & -2.5 & 17.5 & 42.5 & 5 & 55 & 32.22 & 1.43 & \textbf{4.65} \\ \hline
			Sion & -2.5 & 17.5 & 37.5 & 12.5 & 55 & 26.07 & 1.29 & \textbf{5.19} \\ \hline
			Aigle & -2.5 & 17.5 & 40 & 10 & 75 & 32.21 & 1.64 & \textbf{5.36} \\ \hline
		\end{tabular}
	\end{center}
	\label{tab:fenetre_glissante:Resultats_R1_recalibration_fen_gliss}
\end{table}

\begin{table}[htb]
	\caption{Paramètres pour l'humidité et compétence de la méthode R2 après calibration pour la fenêtre temporelle glissante. Le nombre d'analogues du premier niveau d'analogie est donné dans la 6ieme colonne (N$_{1}$) et celui du second niveau dans la 7ieme colonne (N$_{2}$).}
	\begin{center}
		\begin{tabular}{l c c c c c c c c c }
			\hline
			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \multirow{2}{*}{\textbf{N$_{2}$}} & \textbf{CRPSS} &  \multirow{2}{*}{\textbf{$\Delta$}} & \textbf{Gain}\\ 
			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} &  &  & \textbf{(\%)} & & \textbf{(\%)} \\ 
			\hline
			Ulrichen & 5 & 5 & 45 & 2.5 & 110 & 35 & 35.72 & 2.48 & \textbf{7.46} \\ \hline
			Zermatt & 7.5 & 0 & 45 & 2.5 & 80 & 30 & 29.63 & 2.68 & \textbf{9.94} \\ \hline
			Visp & 7.5 & 0 & 45 & 2.5 & 135 & 35 & 30.29 & 2.52 & \textbf{9.07} \\ \hline
			Montana & 5 & 2.5 & 45 & 0 & 110 & 40 & 37.15 & 2.38 & \textbf{6.85} \\ \hline
			Sion & 5 & 5 & 45 & 2.5 & 140 & 50 & 31.68 & 2.32 & \textbf{7.91} \\ \hline
			Aigle & 5 & 2.5 & 45 & 0 & 135 & 45 & 38.50 & 2.55 & \textbf{7.10} \\ \hline
		\end{tabular}
	\end{center}
	\label{tab:fenetre_glissante:Resultats_R2_recalibration_fen_gliss}
\end{table}

>>>>

\runningtitle{Finding Better Analogue Situations at a Sub-Daily Time Step}

@@

\begin{table}[htb]
	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive. The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level (N$_{1}$), which are here different. The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{N$_{2}$} & \textbf{CRPSS} \\
			\hline
			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 60 & 25 & 34.31 \\
			Zermatt & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 55 & 25 & 28.28 \\
			Visp & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 45 & 25 & 28.85 \\
			Montana & 5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 55 & 30 & 36.11 \\
			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
			Aigle & 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z-2MI}
\end{table}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.2cm]{figures/changes_S1_value.pdf} \\
		\includegraphics[width=8.3cm]{figures/changes_S1_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue. (top) Quantiles of the S1 distributions with and without the sliding window. (bottom) Quantiles of the relative improvements of the S1 criteria when using the sliding window.}
	\label{fig:changes_S1}
\end{figure}

@@

\subsection{Changes in the moisture analogy}

When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the candidates situations are not more numerous, as we subsample in the previously $N_{1}$ selected analogues, but the dates may have changed. In contrast to earlier, both a reduction and an increase of the RMSE criterion values are possible. Figure \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values. Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude. Once again, the results for the other stations are similar.

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.1cm]{figures/changes_RMSE_value.pdf} \\
		\includegraphics[width=8.3cm]{figures/changes_RMSE_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the RMSE criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue. (top) Quantiles of the RMSE distributions with and without the sliding window. (bottom) Quantiles of the relative improvements of the RMSE criteria when using the sliding window.}
	\label{fig:changes_RMSE}
\end{figure}

This result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the STW. It means that after the selection of the analogues situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogues in terms of moisture. However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores.

\section{Impact on performance scores}

@@

\begin{table}[htb]
	\caption{Gain en compétence du CRPS sur les deux niveaux d'analogie dû à l'introduction de la fenêtre temporelle glissante.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{\textbf{Station}} & \multicolumn{2}{c}{\textbf{2Z}} & \multicolumn{ 2}{c}{\textbf{2Z-2MI}} \\
			& \textbf{STW} & \textbf{$\Delta$} & \textbf{STW} & \textbf{$\Delta$} \\
			\hline
			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{tab:fenetre_glissante:Gains_CRPSS}
\end{table}

@@

\begin{table}[htb]
	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method with the STW approach.}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{CRPSS} & \textbf{$\Delta$} \\
			\hline
			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 & 31.58 & 2.20 \\
			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 & 24.71 & 2.51 \\
			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 & 25.08 & 1.85 \\
			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 & 32.22 & 1.43 \\
			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 & 26.07 & 1.29 \\
			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 & 32.21 & 1.64 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z_new}
\end{table}

\begin{table}[htb]
	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) with the STW approach. The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level (N$_{1}$), which are here different. The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
	\begin{center}
		\begin{tabular}{l c c c c c c }
			\hline
			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{N$_{2}$} & \textbf{CRPSS} & \textbf{$\Delta$} \\
			\hline
			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 & 35.72 & 2.48 \\
			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 & 29.63 & 2.68 \\
			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 & 30.29 & 2.52 \\
			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 & 37.15 & 2.38 \\
			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 & 31.68 & 2.32 \\
			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 & 38.50 & 2.55 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z-2MI_new}
\end{table}
